---
title: "surnames"
author: "Marcus Torres"
format: revealjs
editor: visual
---

## Intro

The objective in these scripts is to match both 2020 parents data we have available. The first one we did in 2021 during the first phase and the second in 2022

## Installing packages

```{r pack}
library(pacman)
p_load(readr,
       data.table,
       fuzzyjoin,
       dplyr,
       reticulate,
       fuzzywuzzyR,
       janitor,
       genderBR,
       cepespR)
rm(list =ls())
```

## Downloading data

```{r echo = F, results = 'hide', include=FALSE}

#The 2021 data is local

#This was me and octávio
surname_old <- read.csv2("data/surname/all_brazil_parents.csv", sep = ",")

#Anf this one it was danny's
surname_new <- read.csv("https://raw.githubusercontent.com/fdhidalgo/br_political_dynasties/master/output/politician_parents.csv")

#commom names 
name <- fread("https://data.brasil.io/dataset/genero-nomes/nomes.csv.gz" )

```

Lets try to divide the surname table in two

```{r echo = F, results = 'hide', include=FALSE}

surname_new <- unique(surname_new) #cleaning and letting the same
#ids <- as.data.frame(table(surname_new$cand_id))

```

Treating the old surnames

```{r janitor echo = F, results = 'hide', include=FALSE}
surname_old_teste <- surname_old %>% 
                    #lower cases
                     mutate(mae_lower = tolower(mae)) %>% 
                     mutate(pai_lower = tolower(pai)) %>% 
                    #relocate the variable position
                     relocate(pai_lower, .after = pai) %>% 
                     relocate(mae_lower, .after = pai)
```

Using the old data with the most recent one 

```{r name echo = F, results = 'hide', include=FALSE}


inner_mae<- unique(inner_join(surname_old_teste, surname_new, by = c("mae_lower" = "parent_name")))
inner_pai <- unique(inner_join(surname_old_teste, surname_new, by = c("pai_lower" = "parent_name")))

#Join Mother and father
full <- unique(full_join(inner_pai, inner_mae))

#Identify if there is any candidate with more than one
full <- full %>% mutate(id_same = if_else(sq_candidato == cand_id ,1,0))

full %>% 
  group_by(id_same) %>% 
  summarise(id_same = n()) %>% 
  mutate(Rel.Frequency = id_same/sum(id_same)) #Almost 95% have the same ID

#Exclude the ones with different IDs
full<- full %>%  filter(id_same== 1)

```

Trying to guess people's gender

```{r gender}

#Lets first take a sample of it
set.seed(15151) 

#Lets create a sample for that
p_load(pwr)
#pwr.t.test(d=0.80,#for large effect size
#           sig.level=0.05, power=0.80, type="one.sample", alternative="two.sided")

# I did a sample size and the result was 375

#gender <- full %>% sample_frac(0.01)

gender <- full %>% sample_n(375)




#making a test
get_gender(gender$mae)


#getting the father and mothers gender
gender <- gender %>% 
            mutate(gender_mother = get_gender(mae_lower)) %>% 
            mutate(gender_father = get_gender(pai_lower)) %>% 
            relocate(gender_father, .after = pai_lower) %>% 
            relocate(gender_mother, .after = pai_lower)
#In a qualitative analysis in the with the sample, we can see that all the cases with mismatched names were actually the algorithm fault.


#getting gender from Dannys database
surname_new <- surname_new %>% 
            mutate(gender_new = get_gender(parent_name))



#Now lets use all the doc
full <- full %>% 
            mutate(gender_mother = get_gender(mae_lower)) %>% 
            mutate(gender_father = get_gender(pai_lower)) %>% 
            relocate(gender_father, .after = pai_lower) %>% 
            relocate(gender_mother, .after = pai_lower)

male_female <- full %>%
  group_by(gender_mother,gender_father) %>%
  summarize(n())

```

Load the candidates Data

```{r Candidato}

load("/Users/marcustorres/Library/CloudStorage/OneDrive-UniversidadeFederaldePernambuco/UFPE/DOUTORADO/dissertation/dynastiesBR/2020.RData")
rm(Candidato,eng,filho_a_de,filho_de,Filiacao,Orgao,por,text) 

rm("gender",
   "inner_pai",
   "inner_mae",
   "name",
   "surname_old_teste")

dinastias_final <- merge(full, candidatos, by.x = "sq_candidato", by.y = "SQ_CANDIDATO")


#Lets just save the datac
write.csv(dinastias_final, "candidatos_pais_2020.csv")

```



Now we will download CEPESP Candidates Data

```{r cepesp}
#Elected Candidates
federal_elected_2012_2018 <- get_candidates(year = "2018,2014,2010,2006,2002,1998",position = "Deputado Federal", only_elected = T)

state_elected_2012_2018 <- get_candidates(year = "2018,2014,2010,2006,2002,1998",position = "Deputado Estadual", only_elected = T)

mayor_elected_2016_2000 <- get_candidates(year = "2016,2012,2008,2004,2000",position = "Prefeito", only_elected = T)

```




```{r fuzzymathcing}

#Looking municipalities we have the most ammount of candidates with families names
dinastias_final_mun<- dinastias_final %>% group_by(NM_UE) %>% summarise(id_same = n()) 


#Trying to look for places  to possible match
dinastias_final_sample <- dinastias_final %>% 
                          filter(NM_UE == "HOLAMBRA") %>% 
                          select(NM_CANDIDATO,sq_candidato,
                                 mae,
                                 pai,
                                 mae_lower,
                                 pai_lower,
                                 unnormalized_parent_name,
                                 NM_CANDIDATO,
                                 NM_UE
                                 ) %>% unique()

### SAMPLING THE MAYOR
                          
glimpse(mayor_elected_2016_2000)
mayor_elected_2016_2000_sample <- mayor_elected_2016_2000  %>% 
                                filter(DESCRICAO_UE == "HOLAMBRA") %>% 
                                select(ANO_ELEICAO,
                                       DESCRICAO_UE,
                                       NOME_CANDIDATO)



#Remove some data
rm(surname_old,
   surname_new,
   male_female, 
   dinastias_final_mun, 
   dinastias_final_sample,
   dinastias_90514,
   candidatos,
   mayor_elected_2016_2000_sample,
   full)
```
````{r cleaning}
#Before Starting, lets just clean the dinastias_final
glimpse(dinastias_final)
candidatos_2020_pais <- dinastias_final %>% select(sq_candidato,
                                                   mae,
                                                   pai,
                                                   mae,
                                                   mae_lower,
                                                   pai_lower,
                                                   unnormalized_parent_name,
                                                   gender_mother,
                                                   gender_father,
                                                   codigo_tse,
                                                   cpf_child,
                                                   SG_UF,
                                                   SG_UE,
                                                   NM_UE,
                                                   NM_CANDIDATO,
                                                   NM_URNA_CANDIDATO,
                                                   NM_MUNICIPIO_NASCIMENTO)
                                                  
                                        

`````


```{r matching}

match_pref_pai <- merge(candidatos_2020_pais, mayor_elected_2016_2000, by.x = "pai", by.y = "NOME_CANDIDATO") 

%>%  group_by(NM_UE) %>% summarise(id_same = n()) 
```

####################### 

```{r Candidato}
#Parents Matching

#determine 
dinastias_final_sample[is.na(dinastias_final_sample)] <- "empty_string"
#mayor_elected_2016_2000[is.na(surname_new)] <- "empty_string"



match <- mayor_elected_2016_2000_sample %>% 
  stringdist_inner_join( dinastias_final_sample, by = c(NOME_CANDIDATO = "mae")) 



  #group_by(NOME_CANDIDATO) %>%
  slice_min(order_by=dist, n=1)



```
